The problem and promise of scale in animal social multilayer networks

### 2020-08-27 paper/manuscript.Rmd
caps based on

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social distance threshold. For each social distance threshold (5, 25, 50, 75, 100, 250, 500 m), multilayer networks were constructed of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open). Each line represents a single individual and graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes. After 100 m, graph strength continued to increase at a slower rate. Foraging and open layers showed higher variation in graph strength between individuals while forest layers had less variation and lower mean graph strength.

<!-- Figure: metrics by land cover resolution -->
(ref:lcres) Varying spatial scale of land cover raster. For each land cover resolution (100 - 500 m by steps of 100 m), multilayer networks were constructed of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open). A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m). D) Edge overlap of habitat layers across spatial resolutions. Open and forest layers show consistent edge overlap with increasing spatial resolution while foraging shows a sharp decline in edge overlap between 30 m and 600 m. Above 600 m, edge overlap in foraging layers is stable. E) Graph strength within habitat layers across spatial resolutions showing individuals as a separate line and the mean of individuals in bold. Foraging layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution. Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest layers.

<!-- Figure: Time window -->
(ref:temp) Varying temporal scale in multilayer networks. Multilayer networks were generated of caribou social associations within time windows (20 ordinal sample periods) between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`. A) Edge overlap was high between approximately November and May (time windows 1, 6-11, 15-20) and low between approximately June and October (time windows 2-5 and 12-15). B) Ordinal network layers showing unweighted edges between individuals within time windows. Like edge overlap, individuals were more connected between November and May, compared to between June and October.  C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick black lines. Graph strength peaked in time window 9, with noticeable higher strength than the following year.

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open). A) Edge overlap increased for all habitat layers with increasing number of observations. Foraging and open layers had higher edge overlap than forest layers. B) Graph strength within habitat layers with increasing number of observations showing individuals as a separate line and the mean of individuals in bold. Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after ~200 observations. C) Multidegree for all individuals increased with increasing number of observations. Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).

>>>>

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social distance threshold. For each social distance threshold (5, 25, 50, 75, 100, 250, 500 m), multilayer networks based on caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open). Each line represents a single individual and graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes. After 100 m, graph strength continued to increase at a slower rate. Foraging and open layers showed higher variation in graph strength between individuals while forest layers had less variation and lower mean graph strength.

<!-- Figure: metrics by land cover resolution -->
(ref:lcres) Varying spatial scale of land cover raster. For each land cover resolution (100 - 500 m by steps of 100 m), multilayer networks based on caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open). A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m). D) Edge overlap of habitat layers across spatial resolutions. Open and forest layers show consistent edge overlap with increasing spatial resolution while foraging shows a sharp decline in edge overlap between 30 m and 600 m. Above 600 m, edge overlap in foraging layers is stable. E) Graph strength within habitat layers across spatial resolutions showing individuals as a separate line and the mean of individuals in bold. Foraging layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution. Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest layers.

<!-- Figure: Time window -->
(ref:temp) Varying temporal scale in multilayer networks. Multilayer networks based on caribou social associations within time windows (20 ordinal sample periods) between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`. A) Edge overlap was high between approximately November and May (time windows 1, 6-11, 15-20) and low between approximately June and October (time windows 2-5 and 12-15). B) Ordinal network layers showing unweighted edges between individuals within time windows. Like edge overlap, individuals were more connected between November and May, compared to between June and October.  C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick black lines. Graph strength peaked in time window 9, with noticeable higher strength than the following year.

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. Multilayer networks based on a subset of observations (10 - 1000 observations by steps of 10) of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open). A) Edge overlap increased for all habitat layers with increasing number of observations. Foraging and open layers had higher edge overlap than forest layers. B) Graph strength within habitat layers with increasing number of observations showing individuals as a separate line and the mean of individuals in bold. Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after ~200 observations. C) Multidegree for all individuals increased with increasing number of observations. Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).
